Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-10-25 Thesis/chapter/063-discussion.tex
include gen figures
results and discussion planned

\td{ideal objective is to create response surface approximation}\\
\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}\\
\td{too much data as input, dimensionality reduction (PCA) and optimization}\\
\td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
{The primary goal of a screening experiment is to identify the active factors.
A secondary goal is to provide a simple model that captures the essential features of the 
relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{diskussion and outlook}
\td{if i would plan the optimisation again, I would take less input variables (fokus on 
conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
(im nachhinein) steine in den Weg gelegt.}
The space seems to be too big for the small sample size.
Look at relation of space size and sample size here and in Hu2016.
\td{In example of documentation 2 input variables and 1-2 responses initial population=10
, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
iterations (as in actual experiments) lead to suboptimal results.
When plotting input vars  against the response variables, no trend
- The exploration-vs-exploitation parameters of the model were also not set accordingly.}
see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}
Would be easier to fit with single factor at a time variation or latin hyper cuber? 
with same search-space to actual-data ratio
- Would it also be easier for MARS or ML to find fitting function?
plot predictions from EMMA and ML. or rather compare MAE
- the data has a lot of error, but because the production process takes so long and the 
limited time and the chosen optimisation method, the experiments weren't weiderholt
how much variance is in data? 
- The most time consuming part was definitively the prelaminary studies.
this time could have been verkürzt by testing a wide array of diverse recipes from the literature
- The data is spread across the datenraum, such that it is not trivial to 
(1) find the variable with the most variance and 
(2) to fit in order to understand to impact of noise on the data. 

@@

Am besten waere feature extraction (variable x1 hat am meisten einfluss) 
ginge auch wenn man bei pca den einfluss von verschiedenen 
I stand in front of this problem where the solution is to not use as many indep vars von vorne herein. 
- EMMA was finished on 23.02.2021 (make timeline?)
- TODO: check which software versions
-\td{for 1F c(Zr) = 44.6 mmol/L
if n is number of samples, and p is number of input variables, then n >> p 
In this case n\~50 and p\~6 which give n/p=8+1/3
in EMMA documentation example n=55and p=1-2, n/p=55-22.5
plot x vs G and hold all other vars const
write script to do that}
\todo{make sample time line with ipo vs acoh, al vs ag, hg vs doc, ...}
\td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
could have been verhindert durch lesen the docu and more papers more thoughoughly. 
Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}

@@

- \td{I wanted to exhaust the possibilities of EA (not having enough data). i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}
- \td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
- factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest. Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007}
but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
- let's rule out different input variables: \\
does the heating temperature influence the resistance?  no \\
does the heating velocity influence the resistance?  hardly\\
do conc and layers number influence resistance? linear \\
do db velocity and db temperautre influence resistance? how\\
- somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
- "Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
-comparison of population size: 
\verb|see Notes/ga_from_lit_summarj.txt|
what is the minimum of population*generation and what is 10*5

@@

am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
"ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell" \cite{haertler2014statistisch}
Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LINKS}
\begin{itemize}
    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsection{Diskussion}
\subsubsection{Mistakes and Solutions}
This chapter is structured as a letter 
which my present self thinks that would have helped my past self 
if recieved before the start of the practical part of my master practikum:\\

to discuss: results from EMMA or rather which the data present are counter intuitive. 
why lowest conductivity with lowest TCal and why is there a minimum for layers? 
low TDOC results in lower conductivity... okay

Dear Johann,

I know that you (I) won't believe this but I'm you in the future. 
So you are me in the past and I have a few hints on how to avoid some stone in your way 
and how to hopefully be more successful in you master thesis. 
"I make a plan. I break a plan. But I'm never without a plan." - a nice quote which I couln't zuschreiben, but which holds a lot of truth. 
Planning can give you the chance to zoom out and force yourself to get an overview. 
It let's you decide how much time you want to spend on each todo.

The next tip is that at the beginning of a project the research phase shouldn't be underestimated. 
Take time to dig into the basics and discuss with collegues if you have the chance. 
Try to understand the methods you'll use as well as possible. 
Most importantly, high light advantages and disadvantages of the methods and competeing/alternatives. 
Like in a design project. Lay out as many as diverse solutions as possible, 
compare, and ick the best parts.
The research phase let's you learn from other's mistakes and saves a lot of time.

Another important task which preceeds/anti-follows above mentioned is to define the objective as clear as possible.  
%\td{ideal objective is to create response surface approximation}\\
It will help to set a clear goal for each todo, e.g. 
the primary goal of a screening experiment is to identify the active factors.\cite{miller2001using}
Which question should be answered and aufstellen a null Hypothesis. 
This is often very trivial, but let's you focus on the correct path.

The mistake which I regret the most is that I overestimated the vereinfachenden factor of reducing the splits (or discrete points between two extrems, which a variable can take) instead of the reduction of dimensions which eleminates a whole degree of freedom. 
I expected my algorithm of choice to perform magic. 
A measurement to compare different algorithms could be, dimension and ratio of measured sampled to sample space. 
Im vergleich to other algo I used a lot of dimensions and a low ratio.
A low ratio gives rise to a high probability of the data being statistically insignificant, especially if the error is realtively large.

All the best and stay persistent, \\  
Johann \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Mistakes} 
\td{the input vars were not regularized/normalized, naively like a small child eating old food and regretting not informing oneself earlier}\\
\td{too much data as input, dimensionality reduction (PCA) and optimization}\\
\td{pre optimization was used to check if limits where okay, but could also have been used to sieve out factors without impact on response (see miller 2001 \cite{miller2001using} section 1) }
\td{adding a extra variable to optimize was to optimistic and ich hab mir damit eindeutig 
(im nachhinein) steine in den Weg gelegt.}
The space seems to be too big for the small sample size.
%-
Look at relation of space size and sample size here and in Hu2016.:
\td{In example of documentation 2 input variables and 1-2 responses initial population=10
, subsequent population=5, but 10 iterations. Clearly more input varibles and less 
iterations (as in actual experiments) lead to suboptimal results.}
%
- The exploration-vs-exploitation parameters of the model were also not set accordingly.
see \href{https://search.r-project.org/CRAN/refmans/emma/html/emma.html}{source}
%
- the data has a lot of error, but because the production process takes so long and the 
limited time and the chosen optimisation method, the experiments weren't weiderholt
how much variance is in data? 
%
data-points-to-indep-vars ratio as measurement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Next time better}
{The primary goal of a screening experiment is to identify the active factors.
A secondary goal is to provide a simple model that captures the essential features of the 
relationship between these active factors and the response—that is, to identify the active effects. \cite{miller2001using}}
%
\td{if i would plan the optimisation again, I would take less input variables (fokus on 
conc,vdoc and tdoc or even only vdoc and tdoc) which may or may not have multiple maxima.}
%
- The most time consuming part was definitively the prelaminary studies.
this time could have been verkürzt by testing a wide array of diverse recipes from the literature
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Next steps}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{diskussion and outlook}

- The data is spread across the datenraum, such that it is not trivial to 
(1) find the variable with the most variance and 
(2) to fit in order to understand to impact of noise on the data.

@@

Am besten waere feature extraction (variable x1 hat am meisten einfluss) 
ginge auch wenn man bei pca den einfluss von verschiedenen 
I stand in front of this problem where the solution is to not use as many indep vars von vorne herein.

-\td{for 1F c(Zr) = 44.6 mmol/L
if n is number of samples, and p is number of input variables, then n >> p 
In this case n\~50 and p\~6 which give n/p=8+1/3
in EMMA documentation example n=55and p=1-2, n/p=55-22.5
}
\td{longer literature research (first solution,second solution) and PSO wrongly eingeschaetzt, 
could have been verhindert durch lesen the docu and more papers more thoughoughly. 
Ich war geblendet von dem was ich wollte und dadurch nicht realistisch}

@@

- \td{I wanted to exhaust the possibilities of EA (not having enough data). i should have rather einengen the search raum as much as possible (spreading the search room too much) and then do optimisation: fix layer count to 3 fix conc to 3F and fix calc temp and rate (or only use two extreme values)}
- \td{I wanted to let the algorithm show what I already knew instead of letting my a priori knowledge constrain the model before starting.}
- factorial design (classical \gls{doe} is more robust at feature extraction for error laden data \cite{giunta2003overview}
-\td{"Similarly, it is often wise not to plan a comprehensive experiment that involves a large number of factors of interest. Such an experiment presupposes that most or all of the factors are important contributors to changes in the response variable and that they contribute jointly; i.e., that individual factor effects and their interactions are statistically significant and meaningful." - from Gunst2007}
but on the other hand: If one ain't sure a if factor is relevant, the model should be able to detect if there is a influence. - from Haertler2014?
- let's rule out different input variables: \\
does the heating temperature influence the resistance?  no \\
does the heating velocity influence the resistance?  hardly\\
do conc and layers number influence resistance? linear \\
do db velocity and db temperautre influence resistance? how\\
- somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
- "Je grösser nämlich die Anzahl freier Parameter im Modell ist, umso grösser ist der erforderliche Datenumfang und umso ungenauer wir die statistisch gewonnene Aussgae bei gleichem Datenumfang." - Gisela Härtler\cite{haertler2014statistisch}
- \td{The disadvantage of ANOVA is that information is lost because independent variables are assumed categorical even though they are ordinal}
-comparison of population size: 
\verb|see Notes/ga_from_lit_summarj.txt|
what is the minimum of population*generation and what is 10*5

@@

am wichtigsten is das Ziel der untersuchung! \cite{haertler2014statistisch}
"ist das modell fraglich, sollte man die Daten so erheben, als gälte das nächst kompliziertere Modell" \cite{haertler2014statistisch}
Er könnte nun die Unterschiede zwischen den Schulen "statisteisch messen"un den Schuleinfluss in der abschliessenden Analyse "herausrechnen". \cite{haertler2014statistisch}
Eine gefährliche Fehlerquelle ist dei Erwartung eines bestimmten Ergebnisses durch den Experimentator. \cite{haertler2014statistisch}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{LINKS}
\begin{itemize}
    \item stat vs ML \url{https://medium.com/source-institute/ai-vs-statistics-c2485f9df126} and 
    \item https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=3f94b919de45
    \item https://towardsdatascience.com/are-you-aware-how-difficult-your-regression-problem-is-b7dae830652b calculate error/smoothness etc
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Would be easier to fit with single factor at a time variation or latin hyper cuber? 
%with same search-space to actual-data ratio
%- Would it also be easier for MARS or ML to find fitting function?
%plot predictions from EMMA and ML. or rather compare MAE
